Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
Remove references to ``ob'' approaches

The evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $M$ for the \emph{ob} approaches and the scaling parameter $q$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. The \emph{ob} approaches are compared to commonly used early integration approach \emph{early}. %\ja{And BOF?}

The clustering for the \emph{ob} methods is done using $k$-means$++$ \cite{arthur2007k}, an augmented version of $k$-means with a more robust initialization procedure. Three numbers of clusters are tested: $8$, $16$ and $32$.

>>>>

The evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $M$ for the \emph{RbQ} approaches and the scaling parameter $q$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. The \emph{RbQ} approaches are compared to commonly used early integration approach \emph{early}. %\ja{And BOF?}

The clustering for the \emph{RbQ} methods is done using $k$-means$++$ \cite{arthur2007k}, an augmented version of $k$-means with a more robust initialization procedure. Three numbers of clusters are tested: $8$, $16$ and $32$.
